Data Preparation

### 2019-01-10 Data Preparation.Rmd
new text for sections that were moves

### Extracting Text
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.

#### Extracting Overviews

@@

#### Extracting Descriptions

@@

### Extracting Course Manual Text
We create a dataframe from the Corpus:
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

@@

```{r join manuals to d_course}
d_course <- full_join(d_course, d_manual, by = "Code")
```

>>>>

### Extracting Text
In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.

####Course Catalogues
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

##### Extracting Overviews

@@

##### Extracting Descriptions

@@

### Course Manuals
####Extracting Full Text
(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))

Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

@@

Separately, we want to add the manual textual information to`d_course`which contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
```{r join manuals to d_course}
d_course <- full_join(d_course, d_manual, by = "Code")
```
